---
title: "Homwework 8"
author: "Shubham Bhargava"
date: "2024-04-16"
output: github_document
---

```{r}
library(readxl)
News_Website_Dataset <- read_excel("News Website Dataset.xlsx")
#View(News_Website_Dataset)

# correlation  and coefficient B/W Total_revenue and Total Sessions
correlation_coefficient2 <- cor(News_Website_Dataset$Total_revenue, News_Website_Dataset$Total_Sessions)
print(correlation_coefficient2)

plot(News_Website_Dataset$Total_Sessions, News_Website_Dataset$Total_revenue,
     xlab = "Total Sessions", ylab = "Total Revenue",
     main = "Scatter Plot of Total Revenue vs. Total Sessions")

abline(lm(News_Website_Dataset$Total_revenue ~ News_Website_Dataset$Total_Sessions), col = "green")

```
```{r}

correlation_coefficient <- cor(News_Website_Dataset$Total_revenue, News_Website_Dataset$Avg_Session_Duration)

plot(News_Website_Dataset$Avg_Session_Duration, News_Website_Dataset$Total_revenue,
     xlab = "Average Session Duration", ylab = "Total Revenue",
     main = "Scatter Plot of Total Revenue vs. Avg Session Duration")

abline(lm(News_Website_Dataset$Total_revenue ~ News_Website_Dataset$Avg_Session_Duration), col = "purple")

print(paste("Correlation Coefficient between Total Revenue and Avg Session Duration:", correlation_coefficient))

```


### Assignment 8
#### Logistic Regression Analysis
<p>To perform logistic regression analysis, we will use the glm() function.</p>

* Load all necessary packages 
* Load Data. we Used read_excel() function to read data from excel
* Now we will use glm() function to fit a logistic regression model to the data.
* Now use summary() function for logistic regression model to view coefficients, standard errors, z-values, and p-values.
* For Residual Analysis use plot() function to get Plot diagnostic plots, including residuals vs. fitted values, QQ plot of residuals, and scale-location plot, to check for homoscedasticity and normality of residuals.

#### Model Development
```{r}
library(readxl)
library(dplyr)
library(ROCR)
library(pROC)

mydata <- read_excel("News Website Dataset_2.xlsx")
```

```{r}
threshold <- 200

mydata$Revenue_Binary <- ifelse(mydata$Total_revenue > threshold, 1, 0)

logit_model <- glm(Revenue_Binary ~  Total_Sessions
+ Conversion_Rate + Avg_Session_Duration, 
                    data = mydata, 
                    family = binomial)

```

<p>In order to produce a binary result variable based on a threshold, the algorithm first reads and preprocesses a dataset.</p>
<p>It fits a logistic regression model using three predictor variables: <p>Total_Sessions, Conversion_Rate, and Avg_Session_Duration.</p>
Defining the model formula, fitting the model to the data, and producing a summary of the model's coefficients and statistical significance are all steps in this model development process.</p>

#### Model Acceptance
```{r}
summary(logit_model)
anova(logit_model)
```

<p>The coefficients show how each predictor variable is expected to affect the outcome variable's log-odds of falling into the positive class (1).</p>

<p>For instance, the coefficient for Total_Sessions is roughly 0.0002231, meaning that the log-odds of the outcome variable falling into the positive class rises by 0.0002231 units for every unit increase in Total_Sessions.</p>

<p>Conversion_Rate and Avg_Session_Duration have coefficients of 1.1609186 and -0.1110208, respectively..</p>

#### Residual Analysis
```{r}
# Residual Analysis
residuals(logit_model)
plot(logit_model)
```
<p>The function (logit_model) computes the residuals of the fitted logistic regression model. It gives back a vector with the residuals in it.</p>
<p>Diagnostic graphs for the logistic regression model (logit_model) are produced using the plot() function.diagnostic charts, such as the quantile-quantile (Q-Q) plot, leverage plot, and residuals versus fitted values. </p>

#### Prediction
```{r}
predicted_prob <- predict(logit_model, type = "response")

# Create prediction object
predictions <- prediction(predicted_prob, mydata$Revenue_Binary)

roc_curve <- roc(mydata$Revenue_Binary, predicted_prob)

# Plot ROC curve
plot(roc_curve, main = "ROC Curve", col = "yellow", lwd = 2)
abline(a = 0, b = 1, lty = 2, col = "orange")

# Calculate AUC
auc_value <- auc(roc_curve)
cat("AUC:", auc_value, "\n")

# Calculate performance measures
perf <- performance(predictions, "tpr", "fpr")

# Plot ROC curve
plot(perf, main = "ROC Curve", col = "yellow", lwd = 2)
abline(a = 0, b = 1, lty = 2, col = "orange")

# Plot ROC curve
plot(perf, main = "ROC Curve", col = "yellow", lwd = 2, 
     xlab = "False Positive Rate", ylab = "True Positive Rate", 
     xlim = c(0, 1), ylim = c(0, 1))
abline(a = 0, b = 1, lty = 2, col = "orange")  # Diagonal line for reference

# Add AUC value to the plot
auc_value <- performance(predictions, "auc")@y.values[[1]]
text(0.5, 0.5, paste("AUC =", round(auc_value, 2)), col = "#4daf4a", lwd=4)


# Prediction 
new_data <- mydata[1:10, ]
predictions <- predict(logit_model, newdata = new_data, type = "response")
print(predictions)
hist(predictions, breaks = 20, col = "purple", main = "Histogram of Predicted Probabilities")

```

#### Model Accuracy
```{r}
predicted <- predict(logit_model, type = "response")
predicted_binary <- ifelse(predicted > 0.5, 1, 0)
confusion <- table(predicted_binary, mydata$Revenue_Binary)
accuracy <- sum(diag(confusion)) / sum(confusion)
print(accuracy)
```
<p>The code reads a dataset from an Excel file, preprocesses it to create a binary outcome variable based on a threshold, fits a logistic regression model to predict this outcome using three predictor variables, conducts residual analysis, evaluates model performance using ROC curve and calculates AUC, makes predictions for a subset of the data, and assesses model accuracy metrics including accuracy and precision.</p>

