---
title: "Social Media"
author: "Shubham Bhargava"
date: "2024-03-25"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Logistic Regression Analysis
<p>To perform logistic regression analysis, we will use the glm() function.</p>
  
  * Load all necessary packages 
* Load Data. we Used read_excel() function to read data from excel
* Now we will use glm() function to fit a logistic regression model to the data.
* Now use summary() function for logistic regression model to view coefficients, standard errors, z-values, and p-values.
* For Residual Analysis use plot() function to get Plot diagnostic plots, including residuals vs. fitted values, QQ plot of residuals, and scale-location plot, to check for homoscedasticity and normality of residuals.

#### Model Development

```{r}
library(readxl)
library(dplyr)
library(ROCR)
library(pROC)

social_media <- read_excel("social_media_cleaned.xlsx")
social_media_numeric <- select_if(social_media, is.numeric)
```
<p>A logistic regression model is created to estimate the probability of encountering sleep difficulties using Instagram, WhatsApp, OTT, and YouTube usage as predictors.</p>
```{r}
Instagram_lab <- cut(social_media$Instagram, breaks = c(-Inf, 6, Inf), labels = c("Low Usage", "High Usage"))
WhatsApp_lab <- cut(social_media$`Whatsapp/Wechat`, breaks = c(-Inf, 6, Inf), labels = c("Low Usage", "High Usage"))
OTT_lab <- cut(social_media$OTT, breaks = c(-Inf, 6, Inf), labels = c("Low Usage", "High Usage"))
YouTube_lab <- cut(social_media$youtube, breaks = c(-Inf, 6, Inf), labels = c("Low Usage", "High Usage"))

combined_lab <- interaction(WhatsApp_lab, OTT_lab, YouTube_lab)

tfs_table <- xtabs(~ Trouble_falling_asleep + combined_lab, data=social_media) 
tfs_table

logit_model <- glm(Trouble_falling_asleep ~  Instagram + `Whatsapp/Wechat` + OTT + youtube, data = social_media, 
                   family = binomial)

```

<p>The code reads a dataset and preprocesses it to create a binary outcome variable based on a threshold.</p>
  <p>It fits a logistic regression model using three predictor variables: <p>Total_Sessions, Conversion_Rate, and Avg_Session_Duration.</p>
  This model development process involves specifying the model formula, fitting the model to the data, and obtaining a summary of the model's coefficients and statistical significance.</p>

#### Model Acceptance
```{r}
summary(logit_model)
anova(logit_model)
```

<p>The coefficients represent the estimated effect of each predictor variable on the log-odds of the outcome variable being in the positive class (1).</p>

<p>For example, the coefficient for Total_Sessions is approximately 0.0002231, indicating that for each unit increase in Total_Sessions, the log-odds of the outcome variable being in the positive class increases by 0.0002231 units.</p>

<p>The coefficients for Conversion_Rate and Avg_Session_Duration are 1.1609186 and -0.1110208, respectively.</p>

#### Residual Analysis
```{r}
# Residual Analysis
residuals(logit_model)
plot(logit_model)
```
<p>Function calculates the residuals for the fitted logistic regression model (logit_model). It returns a vector containing the residuals.</p>
<p>Plot() function generates diagnostic plots for the logistic regression model (logit_model).diagnostic plots including residuals vs. fitted values, quantile-quantile (Q-Q) plot, and leverage plot  </p>

#### Prediction
```{r}
predicted.social_media <- data.frame(probability.of.hd=logit_model$fitted.values,Instagram=Instagram_lab)
predicted.social_media

xtabs(~ probability.of.hd + Instagram_lab, data=predicted.social_media)
logit_model2 <- glm(Trouble_falling_asleep ~ ., data=social_media, family="binomial")
summary(logit_model2)

predict_data <- predict(logit_model2,newdata=social_media,type="response" )
predict_data
social_media$Trouble_falling_asleep
predict_dataF <- as.factor(ifelse(test=as.numeric(predict_data>0.5) == 0, yes="0", no="1"))
roc(social_media$Trouble_falling_asleep,logit_model2$fitted.values,plot=TRUE)

predicted_prob <- predict(logit_model2, type = "response")

# Create prediction object
predictions <- prediction(predicted_prob, predict_dataF)

roc_curve <- roc(social_media$Trouble_falling_asleep, predicted_prob)

# Plot ROC curve
plot(roc_curve, main = "ROC Curve", col = "green", lwd = 2)
abline(a = 0, b = 1, lty = 2, col = "purple")

auc_value <- auc(roc_curve)
cat("AUC:", auc_value, "\n")

# Calculate performance measures
perf <- performance(predictions, "tpr", "fpr")

# Plot ROC curve
plot(perf, main = "ROC Curve", col = "green", lwd = 2)
abline(a = 0, b = 1, lty = 2, col = "purple")

# Plot ROC curve
plot(perf, main = "ROC Curve", col = "green", lwd = 2, 
     xlab = "False Positive Rate", ylab = "True Positive Rate", 
     xlim = c(0, 1), ylim = c(0, 1))
abline(a = 0, b = 1, lty = 2, col = "purple")  # Diagonal line for reference

# Add AUC value to the plot
auc_value <- performance(predictions, "auc")@y.values[[1]]
text(0.5, 0.5, paste("AUC =", round(auc_value, 2)), col = "#4daf4a", lwd=4)

plot.roc(social_media$Trouble_falling_asleep , logit_model2$fitted.values, percent=TRUE, col="#4daf4a", lwd=4, print.auc=TRUE, add=TRUE, print.auc.y=40)

legend("bottomright", legend=c("Simple", "Non Simple"), col=c("#377eb8", "#4daf4a"), lwd=4) 
```

<p>The logistic regression model estimates the likelihood of experiencing trouble sleeping based on various predictors, including social media usage and user characteristics. However, due to singularities in the data, some coefficients are not defined. The model suggests that characteristics such as "character19!\@s" and "characterpeace" have negligible impact on the likelihood of trouble sleeping, as indicated by their small coefficients close to zero.</p>
<p>For example, individuals with usernames like "masinl", "peace", and "tl868", who spend more time on Instagram, are predicted to have a higher probability (0.75) of experiencing trouble sleeping. Conversely, individuals such as "Patty" and "Bunny", who spend less time on Twitter, are predicted to have a lower probability (0.235) of experiencing trouble sleeping. However, it's important to note that the model coefficients for specific social media platforms like Instagram, LinkedIn, Snapchat, and others are not defined, suggesting that these variables may not significantly contribute to the prediction of trouble sleeping likelihood</p>
  
#### Model Accuracy
```{r}
predicted <- predict(logit_model, type = "response")
predicted_binary <- ifelse(predicted > 0.5, 1, 0)
confusion <- table(predicted_binary, social_media$Trouble_falling_asleep)
accuracy <- sum(diag(confusion)) / sum(confusion)
print(accuracy)
```

<p>The code reads a dataset from an Excel file, preprocesses it to create a binary outcome variables, fits a logistic regression model to predict this outcome using three predictor variables, conducts residual analysis, evaluates model performance using ROC curve and calculates AUC, makes predictions for a subset of the data, and assesses model accuracy metrics including accuracy and precision.</p>
  
  
  